---
output: github_document
---

```{r global_options, include = F}
knitr::opts_chunk$set(warning = F, message = F, dev = 'svg')

```
# CSGO Matches Analysis

To analyze your matches:

* Go to your csgo competitive match history and save the html webpage\*
* Run the scraper on the html
* Run the R analysis on the resulting sqlite file (wip)

\* This
[reddit post](https://www.reddit.com/r/GlobalOffensive/comments/8mbtjx/how_to_check_your_personal_game_data_for_banned/)
contains a plugin for helping load all the matches. (from 3KliksPhillip)
[video](https://youtu.be/AJyemS9hl50))

### Running the Scrapper
```bash
$ git clone https://github.com/BorisNikulin/csgo-matches-analyzer.git
$ cd ./csgo-matches-analyzer/data-scraper
$ stack build
$ stack exec scraper-exe -- --help
```

Note: The R analysis assumes the database is called `csgo.db` and is located
inside `data-scraper`.



## Analysis (wip)

```{r import_data}
library(readr)
library(DBI)
library(lubridate)
library(dplyr)
library(tidyr)
library(glue)

vars <- read_csv('secrets/vars.csv',
	col_types = cols(col_character(), col_character())
	)
id1 <- vars$MY_ID
id2 <- vars$FRIEND_ID
p.name <- glue("CASE WHEN p.steam_id = {id1} THEN 'Me' WHEN {id2} THEN 'Friend' END AS name")

# Sql with variable Interpolation utility func
# idk why glue_sql doesnt work
# however it quotes interpolated variables which i dont want
si <- . %>% glue() %>% sql()

con <- dbConnect(RSQLite::SQLite(), './data-scraper/csgo.db')
```
```{r plot}
library(ggplot2)

tbl(con, si("
	SELECT {p.name}, pl.start_time
	FROM player p
	INNER JOIN played_in pl ON p.steam_id = pl.pid
	WHERE
		p.steam_id = {id2} OR
		p.steam_id = {id1}
	")) %>%
	collect() %>%
	mutate(name = as.factor(name)) %>%
	mutate(start_time = ymd_hms(start_time)) %>%
	ggplot(aes(start_time)) +
	geom_histogram() +
	facet_grid(name~.)
```

```{r avg-kills}
tbl(con, si("
	SELECT AVG(pl.kills) AS AvgDayKills, pl.start_time, {p.name}
	FROM player p
	INNER JOIN played_in pl ON p.steam_id = pl.pid
	WHERE
		p.steam_id = {id1} OR
		p.steam_id = {id2}
	GROUP BY p.steam_id, pl.start_time
	")) %>%
	collect() %>%
	mutate(start_time = ymd_hms(start_time)) %>%
	ggplot(aes(start_time, AvgDayKills)) +
	geom_line() +
	geom_smooth() +
	facet_grid(name~.)
```

```{r kill-difference}
tbl(con, si("
	SELECT pl1.start_time, (pl1.kills - pl2.kills) AS 'Difference'
	FROM player p1, player p2
	INNER JOIN played_in pl1 ON p1.steam_id = pl1.pid
	INNER JOIN played_in pl2 ON p2.steam_id = pl2.pid
	WHERE
	  p1.steam_id = {id1} AND
	  p2.steam_id = {id2} AND
	  pl1.start_time = pl2.start_time AND
	  pl1.map = pl2.map AND
	  pl1.duration = pl2.duration
	GROUP BY pl1.start_time
	")) %>%
	collect() %>%
	mutate(start_time = ymd_hms(start_time)) %>%
	ggplot(aes(start_time, Difference)) +
	geom_line() +
	geom_smooth()
```

```{r win-ratio}
data_win_ratio_per_kill_map <- tbl(con, si("
	SELECT {p.name}, pl.kills, m.map, AVG(win.DidWin) AS WinRate, COUNT(win.DidWin) AS Weight
	FROM player p
	INNER JOIN played_in pl ON p.steam_id = pl.pid
	INNER JOIN match m ON
		pl.map = m.map AND
		pl.start_time = m.start_time AND
		pl.duration = m.duration
	INNER JOIN (
		SELECT p.steam_id, m.map, m.start_time, m.duration,
			CASE
				WHEN pl.team = 0 AND m.score_team_a = 16 THEN 1
				WHEN pl.team = 1 AND m.score_team_b = 16 THEN 1
				WHEN m.score_team_a = 16 OR m.score_team_b = 16 then 0
			END as DidWin
		FROM player p
		INNER JOIN played_in pl ON p.steam_id = pl.pid
		INNER JOIN match m ON
			pl.map = m.map AND
			pl.start_time = m.start_time AND
			pl.duration = m.duration
	) win ON
		p.steam_id = win.steam_id AND
		m.map = win.map AND
		m.start_time = win.start_time AND
		m.duration = win.duration
	WHERE
		p.steam_id = {id1} OR
		p.steam_id = {id2}
	GROUP BY p.steam_id, pl.kills, m.map
	")) %>%
	collect() %>%
	drop_na()

data_win_ratio_per_kill_map %>%
	add_count(name, map) %>%
	filter(n != 1) %>%
	ggplot(aes(kills, WinRate)) +
	geom_smooth() +
	geom_line() +
	facet_grid(name ~ map) +
	guides(alpha = FALSE)

data_win_ratio_per_kill <- data_win_ratio_per_kill_map %>%
	group_by(name, kills) %>%
	summarise(
		WinRate = weighted.mean(WinRate, Weight),
		Weight = sum(Weight))

ggplot(data_win_ratio_per_kill, aes(kills, WinRate)) +
	geom_point() +
	geom_smooth() +
	geom_line() +
	facet_grid(name~.)
```

Hypothesis: I do *better* when I play solo than when I play with my friend.
We will use a Welch's t test to compare performance of the two distributions.
The variable we will consider is the score since it's an easy and comprehensive enough
total score.

```{r ttest}
performance_solo <- tbl(con, si("
	SELECT pl1.kills, pl1.assists, pl1.deaths,
		pl1.mvps, pl1.hsp, pl1.score
    FROM player p1, player p2
    INNER JOIN played_in pl1 ON p1.steam_id = pl1.pid
    INNER JOIN played_in pl2 ON p2.steam_id = pl2.pid
    WHERE
      p1.steam_id = {id1} AND
      p2.steam_id <> {id2} AND
      pl1.start_time = pl2.start_time AND
      pl1.map = pl2.map AND
      pl1.duration = pl2.duration
    GROUP BY pl1.start_time
	")) %>% collect()

performance_with_friend <- tbl(con, si("
	SELECT pl1.kills, pl1.assists, pl1.deaths,
		pl1.mvps, pl1.hsp, pl1.score
    FROM player p1, player p2
    INNER JOIN played_in pl1 ON p1.steam_id = pl1.pid
    INNER JOIN played_in pl2 ON p2.steam_id = pl2.pid
    WHERE
      p1.steam_id = {id1} AND
      p2.steam_id = {id2} AND
      pl1.start_time = pl2.start_time AND
      pl1.map = pl2.map AND
      pl1.duration = pl2.duration
    GROUP BY pl1.start_time
	")) %>% collect()

for(i in 1:ncol(performance_solo))
{
	print(names(performance_solo)[i])
	print(t.test(performance_solo[[i]], performance_with_friend[[i]]))
}
```
